*** Clustering
---
Because of the input data file format, use read.table to read in movieLens.txt, assign columnNames, mask unneeded columns and remove duplicate observations.
```{r}
movies = read.table("./Data/movieLens.txt", header=F, sep="|",quote="\"")

colnames(movies) = c("ID", "Title", "ReleaseDate", "VideoReleaseDate", "IMDB", "Unknown", "Action", "Adventure", "Animation", "Childrens", "Comedy", "Crime", "Documentary", "Drama", "Fantasy", "FilmNoir", "Horror", "Musical", "Mystery", "Romance", "SciFi", "Thriller", "War", "Western")

movies$ID = NULL
movies$ReleaseDate = NULL
movies$VideoReleaseDate = NULL
movies$IMDB = NULL

movies = unique(movies)
```
How many of the movies are comedies?
```{r}
nrow(movies[which(movies$Comedy==1),])
```
First define "distances" then use it to do hierarchical clustering
```{r}
distances = dist(movies[2:20], method = "euclidean")

clusterMovies = hclust(distances, method = "ward.D") #hierarchical clustering
plot(clusterMovies)
```
Try plotting to a file
```{r}
pdf("./Data/clusterMovies.pdf", width=40, height=15)
plot(clusterMovies)
dev.off()
```
And just about when you think you are going to die from boring-graphics-boredom, go ape
```{r}
library('ape')
plot(as.phylo(clusterMovies), 
     type = "fan", 
     tip.color = hsv(runif(15, 0.65, 0.95), 1, 1, 0.7), 
     edge.color = hsv(runif(10, 0.65, 0.75), 1, 1, 0.7), 
     edge.width = runif(20, 0.5, 3), 
     use.edge.length = TRUE, 
     col = "gray80")

mypal = c("#556270", "#4ECDC4", "#1B676B", "#FF6B6B", "#C44D58") # vector of colors
clus5 = cutree(clusterMovies, 125)  # cutting dendrogram in 25 clusters

plot(as.phylo(clusterMovies), type = "fan", tip.color = mypal[clus5], label.offset = 1, col = "red")
```
Add some sparcl to the dendogram
```{r}
library(sparcl)
# colors the leaves of a dendrogram
y = cutree(clusterMovies, 3)
ColorDendrogram(clusterMovies, y = y, labels = names(y), main = "My Cluster", branchlength = 80)
```
Rotate to look at it another way
```{r}
library('ggdendro')
ggdendrogram(clusterMovies, rotate = TRUE, size = 4, theme_dendro = FALSE, color = "tomato")
```
Assign observations to clusters and look at similarites between groups.  If someone liked the movie, 'Men in Black', what other movies might they like?
```{r}
clusterGroups = cutree(clusterMovies, k = 10)
tapply(movies$Action, clusterGroups, mean)
tapply(movies$Romance, clusterGroups, mean)

subset(movies, Title=="Men in Black (1997)")
clusterGroups[257]
cluster2 = subset(movies, clusterGroups==2)
```
