*** CLUSTERnotF
---
Because of the input data file format, use read.table to read in movieLens.txt, assign columnNames, mask unneeded columns and remove duplicate observations.
```{r}
movies = read.table("./Data/movieLens.txt", header=F, sep="|",quote="\"")

colnames(movies) = c("ID", "Title", "ReleaseDate", "VideoReleaseDate", "IMDB", "Unknown", "Action", "Adventure", "Animation", "Childrens", "Comedy", "Crime", "Documentary", "Drama", "Fantasy", "FilmNoir", "Horror", "Musical", "Mystery", "Romance", "SciFi", "Thriller", "War", "Western")

movies$ID = NULL
movies$ReleaseDate = NULL
movies$VideoReleaseDate = NULL
movies$IMDB = NULL

movies = unique(movies)
```
How many of the movies are comedies?
```{r}
nrow(movies[which(movies$Comedy==1),])
```
First define "distances" then use it to do hierarchical clustering
distances = dist(movies[2:20], method = "euclidean")

clusterMovies = hclust(distances, method = "ward.D") #hierarchical clustering
plot(clusterMovies)
```
Assign observations to clusters and look at similarites between groups.  If someone liked the movie, 'Men in Black', what other movies might they like?
```{r}
clusterGroups = cutree(clusterMovies, k = 10)
tapply(movies$Action, clusterGroups, mean)
tapply(movies$Romance, clusterGroups, mean)

subset(movies, Title=="Men in Black (1997)")
clusterGroups[257]
cluster2 = subset(movies, clusterGroups==2)

