---
___SNA
---
Clean up the environment and load edges.csv (the endpoints of edges in our network) and users.csv (contains information about the Facebook users, who are the vertices).
```{r}
rm(list=ls())
edges <- read.csv("./Data/edges.csv")
users <- read.csv("./Data/users.csv")
```
What is the average number of friends per user?
```{r}
# nrow(edges)/(nrow(users)) #NOPE not 2.474576
# nrow(edges)/(nrow(users) -1 ) #NOPE not 2.517241
ave(degree(g))

library('ggplot2')
library('igraph')

```
Have both gendersA&B attended both schools?
```{r}
table(users$gender, users$school)
table(users$school, users$locale)
```
Make an undirected graph with this data
```{r}
g <- graph.data.frame(edges, FALSE, users)
plot(g, vertex.size=5, vertex.label=NA)
```
How many connected islands are there? How many lonely souls?
```{r}
cluster.distribution(g)  #grrr
infomap.community(g)  #cool, but no help here
```
How many FB users have more than 10 friends?
```{r}
table(degree(g) >= 10)
```
Make the dot size reflect the number of friends
```{r}
V(g)$size = degree(g)/2+2
plot(g, vertex.label=NA)
```
What is the largest & smallest sizes assigned to any nodes?
```{r}
sort(V(g)$size)
summary(degree(g))
```
Assign gender color to vertices.  What is the most popular gender (A or B)?
V(g)$color = "black"
V(g)$color[V(g)$gender == "A"] = "red"
V(g)$color[V(g)$gender == "B"] = "gray"
plot(g, vertex.label=NA)
```
Color the vertices based on the school attended.
```{r}
V(g)$color = "grey"
V(g)$color[V(g)$school == "A"] = "maroon1"
V(g)$color[V(g)$school == "B"] = "yellow"
V(g)$color[V(g)$school == "AB"] = "cyan"
plot(g, vertex.label=NA)
```
Color the vertices based on the locale of the user
```{r}
V(g)$color = "black"
V(g)$color[V(g)$locale == "A"] = "magenta"
V(g)$color[V(g)$locale == "B"] = "chartreuse"
plot(g, vertex.label=NA, edge.width = 3)
#rglplot(g, vertex.label=NA)  #rgl doesn't play well with R 3.1.3
```
`
