-----------
##########################
# Word Cloud
########################
-----------
Clean it up and load data ensuring strings remain strings
```{r}
rm(list=ls())
setwd('~/EdX/AE')
tweets = read.csv('./Data/tweets.csv', stringsAsFactors=F)
```
Create a corpus using the Tweet variable
```{r}
library('tm')
corpus = Corpus(VectorSource(tweets$Tweet))
```
Convert corpus to lowercase, remove punct and English-language stopwords
```{r}
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, PlainTextDocument)
corpus = tm_map(corpus, content_transformer(removePunctuation))
corpus = tm_map(corpus, removeWords, c("apple",stopwords("english")))

corpus = tm_map(corpus, PlainTextDocument)
```
Build a DTM from corpus
```{r}
frequencies = DocumentTermMatrix(corpus)
```
Convert DTM to dataFrame (allTweets)
```{r}
allTweets = as.data.frame(as.matrix(frequencies))
```
How many unique terms?
```{r}
unique(frequencies)  #
```
Build wordcloud from the DTM, using vector of words (colnames(xxx) and word frequencies (colSums(xxx)))
```{r}
library('wordcloud')
wordcloud(colnames(allTweets), 
          colSums(allTweets), 
          scale=c(2,0.25),
          colors='green', 
          #colors=brewer.pal(8,"Greys")) #greyscale
          #colors=brewer.pal(4, "YlOrRd")) #sequential palette
          #colors=brewer.pal(8, "Set2")) #qualitative palette
          #colors=brewer.pal(8, "Accent")) #qualitiative palette
          random.color=F)
```  
when random.color=T, no info conveyed via color
```{r}
wordcloud(colnames(allTweets), 
          colSums(allTweets), 
          colors='blue', 
          scale=c(2,0.25),
          random.color=T)
```
A wordcloud of all the tweets with a 0.5 rot.per
```{r}
wordcloud(
  colnames(allTweets),
  colSums(allTweets), 
  scale=c(2,0.25), #max.words=100, 
  #random.order=F, #most freq words together in center
  random.order=T, 
  #rot.per=0.1, #default rot.per = 0.1
  rot.per=0.5, #rot.per controls the frequency of vertical elements
  use.r.layout=FALSE, 
	colors=brewer.pal(9, "Blues")[c(-1, -2, -3, -4)],
	ordered.colors=FALSE)
```
Make a wordcloud of tweets with a negative sentiment (sentiment== -1)
```{r}
negativeTweets = subset(allTweets, tweets$Avg <= -1)
wordcloud(
  colnames(negativeTweets),
  colSums(negativeTweets), 
  scale=c(2,0.25), #max.words=100, 
  #random.order=F, #most freq words together in center
  random.order=T, 
  #rot.per=0.1, #default rot.per = 0.1
  rot.per=0.5, #rot.per controls the frequency of vertical elements
  use.r.layout=FALSE, 
  colors=brewer.pal(4, "YlOrRd"))
```
Check out the position of the most frequent words when random.order=F  - centrally located?
```{r}
wordcloud(colnames(negativeTweets), colSums(negativeTweets), random.order=F, colors = "purple", use.r.layout=FALSE, ordered.colors = T)
```
versus the position of the most frequent words when random.order=T
```{r}
wordcloud(colnames(negativeTweets), colSums(negativeTweets), random.order=T, colors = "purple", use.r.layout=FALSE, ordered.colors = T)

```

