---
---
Clean up environment and read in stocks data and determine proportion of stocks with positive returns in December
```{r}
rm(list=ls())

setwd('~/EdX/AE')
stocks = read.csv('./Data/stocksCluster.csv', header=T)
dim(stocks)
nrow(stocks)
names(stocks)
str(stocks)
```
Determine proportion of stocks with positive returns in December
```{r}
#nrow(subset(stocks, stocks$voting == "December" & stocks$returns > 0))/nrow(stocks)
mean(stocks$PositiveDec)
#
decTable = table(stocks$PositiveDec)
decTable[2]/sum(decTable)
#
prop.table(table(stocks$PositiveDec >0))
```
What is the max pairwise correlation between variables in dataset?
```{r}
sort(cor(stocks[1:11], use='pairwise.complete.obs'))
```
Which month has largest mean return?  If I wanted to find the max min mean return month, 
```{r}
summary(stocks) #or
#
apply(stocks,2,mean) #running over the columns
#
mean(stocks$ReturnJan);  mean(stocks$ReturnFeb); mean(stocks$ReturnMar); mean(stocks$ReturnApr); mean(stocks$ReturnMay); mean(stocks$ReturnJun); mean(stocks$ReturnJul); mean(stocks$ReturnAug); mean(stocks$ReturnSep); mean(stocks$ReturnOct); mean(stocks$ReturnNov)
```
___Logistic Regression
Set seed to 144 and make a 70/30 split (stocksTrain,stocksTest). Create a logistic response model (StocksModel) to predict PositiveDec.
```{r}
library('caTools')
set.seed(144)
spl = sample.split(stocks$PositiveDec, SplitRatio = 0.7)
stocksTrain = subset(stocks, spl == TRUE)
stocksTest = subset(stocks, spl == FALSE)
#stocksModel=logfit
stocksModel = glm(PositiveDec ~., data = stocksTrain, family='binomial')
ptable=table(predict(stocksModel, type='response') > 0.5, stocksTrain$PositiveDec)
accuracy =sum(diag(ptable))/sum(ptable)
ptable
accuracy
```
What is the overall accuracy of the model on test set with a 0.5 threshold?
```{r}
PredictTest = predict(stocksModel, newdata=stocksTest, type="response")
pTable = table(stocksTest$PositiveDec, PredictTest > 0.5)
accuracy = sum(diag(pTable))/sum(pTable)
#
sum((predict(stocksModel,type="response", newdata=stocksTest)>0.5) == stocksTest$PositiveDec)/length(stocksTest$PositiveDec)
```
What is the accuracy of the baseline model on the test set?
```{r}
sum( 1 == stocksTest$PositiveDec) / length(stocksTest$PositiveDec)
#
table(stocksTest$PositiveDec)
#
pTable= table(stocksTest$PositiveDec)
max(pTable)/sum(pTable)
```
___ Clustering
First, remove dependent variable
```{r}
limitedTrain = stocksTrain
limitedTrain$PositiveDec = NULL
limitedTest = stocksTest
limitedTest$PositiveDec = NULL
```
Normalize features
```{r}
library('caret')
preproc = preProcess(limitedTrain)
normTrain = predict(preproc, limitedTrain)
normTest = predict(preproc, limitedTest)
```
What is the mean of factor ReturnJan in normalized training set? In the test set?
```{r}
mean(normTrain$ReturnJan)
mean(normTest$ReturnJan)
```
Run 3 cluster Kmeans on normTrain with a seed set of 144
```{r}
set.seed(144)
km = kmeans(normTrain, centers=3)
table(km$cluster)
```
Use flexclust to get training set and test set assignments.  How many test set observations were assigned to cluster 2?
```{r}
library('flexclust')
km.kcca = as.kcca(km, normTrain)
clusterTrain = predict(km.kcca)
clusterTest = predict(km.kcca, newdata=normTest)
table(clusterTest)
```
Cluster-specific predictions.  Build data frames stocksTrain[1:3] and stocksTest[1:3] using the assignemnts above
```{r}
stocksTrain1 = subset(stocksTrain, clusterTrain==1)
stocksTrain2 = subset(stocksTrain, clusterTrain==2)
stocksTrain3 = subset(stocksTrain, clusterTrain==3)
stocksTest1 = subset(stocksTest, clusterTest==1)
stocksTest2 = subset(stocksTest, clusterTest==2)
stocksTest3 = subset(stocksTest, clusterTest==3)
mean(stocksTrain1$PositiveDec); mean(stocksTrain2$PositiveDec); mean(stocksTrain3$PositiveDec)
```
Logistic Regression Model Building
```{r}
stocksModel1 = glm(PositiveDec ~ ., data=stocksTrain1,family="binomial")
stocksModel2 = glm(PositiveDec ~ ., data=stocksTrain2, family="binomial")
stocksModel3 = glm(PositiveDec ~ ., data=stocksTrain3, family="binomial")
```
Which variables have a positive sign for the coefficient in at least one of StocksModel1, StocksModel2, and StocksModel3 and a negative sign for the coefficient in at least one of StocksModel1, StocksModel2, and StocksModel3?
```{r}
stocksDF <- data.frame("stocksModel1" = stocksModel1$coefficients, "stocksModel2" = stocksModel2$coefficients, "stocksModel3" = stocksModel3$coefficients)
stocksDF
```
What is the overall accuracy of model1 on the testset with a 0.5 threshold?
```
pred1 <- (predict(stocksModel1, type="response", newdata = stocksTest1) > 0.5)
acc1 <- sum( pred1 == stocksTest1$PositiveDec)/ length(stocksTest1$PositiveDec)
acc1
```
What is the overall accuracy of model2 on the testset with a 0.5 threshold?
```{r}
pred2 <- (predict(stocksModel2, type="response", newdata = stocksTest2) > 0.5)
acc2 <- sum( pred2 == stocksTest2$PositiveDec)/ length(stocksTest2$PositiveDec)
acc2
```
What is the overall accuracy of model1 on the testset with a 0.5 threshold?
```{r}
pred3 <- (predict(stocksModel3, type="response", newdata = stocksTest3) > 0.5)
acc3 <- sum( pred3 == stocksTest3$PositiveDec)/ length(stocksTest3$PositiveDec)
acc3
#
PredictTest1 = predict(stocksModel1, newdata = stocksTest1, type="response")
table(stocksTest1$PositiveDec, PredictTest1 > 0.5)
pTable1 = table(stocksTest1$PositiveDec, PredictTest1 > 0.5)
accuracy1 = sum(diag(pTable1))/sum(pTable1)
accuracy1

PredictTest2 = predict(stocksModel2, newdata = stocksTest2, type="response")
table(stocksTest2$PositiveDec, PredictTest2 > 0.5)
pTable2 = table(stocksTest2$PositiveDec, PredictTest2 > 0.5)
accuracy2 = sum(diag(pTable2))/sum(pTable2)
accuracy2

PredictTest3 = predict(stocksModel3, newdata = stocksTest3, type="response")
table(stocksTest3$PositiveDec, PredictTest3 > 0.5)
pTable3 = table(stocksTest3$PositiveDec, PredictTest3 > 0.5)
accuracy3 = sum(diag(pTable3))/sum(pTable3)
accuracy3
```
Overall accuracy?  Combine all predictions and all outcomes.
```{r}
pred <- c(pred1, pred2, pred3)
actual <- c(stocksTest1$PositiveDec, stocksTest2$PositiveDec, stocksTest3$PositiveDec)
sum(actual == pred)/length(actual)
#
AllPredictions = c(PredictTest1, PredictTest2, PredictTest3)
AllOutcomes = c(stocksTest1$PositiveDec, stocksTest2$PositiveDec, stocksTest3$PositiveDec)
table(AllOutcomes, AllPredictions > 0.5)
pTable = table(AllOutcomes, AllPredictions > 0.5)
accuracy = (sum(diag(pTable))/sum(pTable))
accuracy
```
