---
title: "Visualisations Election by State - EdX"
author: "Lin Crampton"
date: "19 Apr 2015"
output: html_document
---
Clean up environment, load and examine/plot statesMap mercator 
```{r initializeStatesMap}
rm(list=ls())
setwd('~/EdX/AE')
library('ggplot2')
library('ggmap')
library('maps')
statesMap = map_data("state")
str(statesMap)
table(statesMap$group)
#how many different groups are there
length(unique(statesMap$group))

ggplot(statesMap, aes(x = long, y = lat, group = group)) + 
  geom_polygon(fill = "white", color = "blue") + 
  coord_map("mercator")
```
Read in polling data, split into Train(2004&2008) and Test(2012)
```{r trainTestData}
polling = read.csv("./Data/PollingImputed.csv")
Train = subset(polling, polling$Year %in% c(2004, 2008))
Test = subset(polling, polling$Year==2012)
```
Train logistic response; determine 0.5 accuracy on Test
```{r logRtrainTest}
mod2 = glm(Republican~SurveyUSA+DiffCount, data=Train, family="binomial")
TestPrediction = predict(mod2, newdata=Test, type="response")
TestPredictionBinary = as.numeric(TestPrediction > 0.5)
predictionDataFrame = data.frame(TestPrediction, TestPredictionBinary, Test$State)

table(predictionDataFrame$TestPredictionBinary)
mean(TestPrediction)
```
Merge predictionDataFrame w statesMap by region, ensuring factor consistency
```{r mapNpredictionMerge}
predictionDataFrame$region = tolower(predictionDataFrame$Test.State)
predictionMap = merge(statesMap, predictionDataFrame, by = "region")
predictionMap = predictionMap[order(predictionMap$order),]
```
Plot merged predictions
```{r electionPredictionsInColor}
ggplot(predictionMap, aes(x = long, y = lat, group = group, fill = TestPredictionBinary)) + ggtitle("ElectionPreds - Light=Repub, Dark=Demo") + geom_polygon(color = "black")

ggplot(predictionMap, aes(x = long, y = lat, group = group, fill = TestPrediction))+ 
	geom_polygon(color = "black", alpha=0.3) + 
	ggtitle("Gradient Fill - Rep=Red, Demo=Blue") +
	scale_fill_gradient(low = "blue", high = "red", guide = "legend", breaks= c(0,1), 
	labels = c("Democrat", "Republican"), name = "Prediction 2012")

ggplot(predictionMap, aes(x = long, y = lat, group = group, fill = TestPredictionBinary))+ 
  geom_polygon(color = "black") +
  ggtitle("Binary Test Prediction - Rep=Red, Demo=Blue") +
  scale_fill_gradient(low = "blue", high = "red", guide = "legend", breaks= c(0,1), labels = c("Democrat", "Republican"), name = "Prediction 2012")
```
Our model didn't do too good of a job at predicting Florida.  How certain was our model?  How good was the model on California, and how certain there?
```{r andFloridaGoes}
predictionDataFrame$TestPrediction[which(predictionDataFrame$Test.State=="Florida")]
predictionDataFrame$TestPrediction[which(predictionDataFrame$Test.State=="California")]
```
Try geom_polygon options
```{r geom_polygonOptions}
ggplot(predictionMap, aes(x = long, y = lat, group = group, fill = TestPredictionBinary))+ 
  geom_polygon(color = "black", alpha=0.3) +
  ggtitle("Alpah = 0.3") +
  scale_fill_gradient(low = "blue", high = "red", guide = "legend", breaks= c(0,1), labels = c("Democrat", "Republican"), name = "Prediction 2012")

ggplot(predictionMap, aes(x = long, y = lat, group = group, fill = TestPredictionBinary))+ 
  geom_polygon(color = "black", linetype=3) +
  ggtitle("Dashed Lines - Linetype - 5") +
  scale_fill_gradient(low = "blue", high = "red", guide = "legend", breaks= c(0,1), labels = c("Democrat", "Republican"), name = "Prediction 2012")

ggplot(predictionMap, aes(x = long, y = lat, group = group, fill = TestPredictionBinary))+ 
  geom_polygon(color = "black", size=3) +
  ggtitle("Size=3") +
  scale_fill_gradient(low = "blue", high = "red", guide = "legend", breaks= c(0,1), labels = c("Democrat", "Republican"), name = "Prediction 2012")

ggplot(predictionMap, aes(x = long, y = lat, group = group, fill = TestPredictionBinary))+ 
  geom_polygon(color = "black") +
  ggtitle("Binary Test Prediction - Rep=Red, Demo=Blue") +
  scale_fill_gradient(low = "blue", high = "red", guide = "legend", breaks= c(0,1), labels = c("Democrat", "Republican"), name = "Prediction 2012")
```