*** CLUSTER
---
Read in flower data (flower.csv) and change datatype to matrix to vector.  Note that it would not be a good idea to go directly from csv to vector, because would lose nice square matrix structure
```{r initialise}
flower = read.csv("./Data/flower.csv", header=FALSE)
#str(flower)
flowerMatrix = as.matrix(flower)
#str(flowerMatrix)
flowerVector = as.vector(flowerMatrix)
#str(flowerVector)
```
Compute a hierarchical (euclidean) distance matrix and examine effect of selecting 3 clusters.
```{r euclideanDistanceMatrix}
distance = dist(flowerVector, method = "euclidean")
clusterIntensity = hclust(distance, method="ward.D")
plot(clusterIntensity)
```
```{r clusterFlowers, error=T}
library('stats')
plot(clusterIntensity, k=3, border="red")
rect.hclust(clusterIntensity, k = 3, border = "red")
flowerClusters = cutree(clusterIntensity, k = 3)
cutThree <- cutree(clusterIntensity, k=3); table(cutThree)
cutFour <- cutree(clusterIntensity, k=4); table(cutFour)
cutFive  <- cutree(clusterIntensity, k=5); table(cutFive)
#flowerClusters
```
```{r slightlyMoreVisibleClusters}
hcd = as.dendrogram(clusterIntensity)
plot(cut(hcd, h=0.3)$upper, 
     main="Upper tree of cut at h=0.3")
plot(cut(hcd, h=0.3)$lower[[2]], 
     main="Second branch of lower tree with cut at h=0.3")
```
```{r improveDendrogramApe}
library('ape')
plot(as.phylo(clusterIntensity), cex=0.1, label.offset=1)
plot(as.phylo(clusterIntensity), type = "unrooted",cex=0.1)
plot(as.phylo(clusterIntensity), type = "fan", cex=0.01, label.offset=0.05)
```
```{r improveDendrogramGGdendro}
library('ggdendro')
ggdendrogram(clusterIntensity, theme_dendro=F)
ggdendrogram(clusterIntensity, rotate=T, size=4, theme_dendro=F)
```
Find the mean intensity value for each cluster
```{r meanIntensityPerCluster}
tapply(flowerVector, flowerClusters, mean)
```
Use dim to convert flowerClusters vector to matrix, then examine how image was segmented using image function.
```{r examineImage}
dim(flowerClusters) = c(50,50)
image(flowerClusters, axes = FALSE)
```
Read in an MRI datafile and transform into a matrix into a vector
```{r MRIdata2vector}
healthy = read.csv("Data/healthy.csv", header=FALSE)
healthyMatrix = as.matrix(healthy)
#str(healthyMatrix)
image(healthyMatrix,axes=FALSE,col=grey(seq(0,1,length=256)))
healthyVector = as.vector(healthyMatrix)
```
Is it possible to compute the distance matrix using hierarchical clustering? Kmeans with a maximum 1000 iterations?
```{r KmeansDistance, error=T}
distance = dist(healthyVector, method = "euclidean") # 2 big
#str(healthyVector)
k = 5
set.seed(1)
KMC = kmeans(healthyVector, centers = k, iter.max = 1000)
#str(KMC)
```
Make a variable healthyClusters with kmeans cluster info. Convert healthyClusters to a matrix.  Make sure it is the same size as healthyMatrix.
```{r KmeansCompareClusters}
healthyClusters = KMC$cluster
KMC$centers[2]
dim(healthyClusters) = c(nrow(healthyMatrix), ncol(healthyMatrix))
image(healthyClusters, axes = FALSE, col=rainbow(k))
```
Use this MRI image to identify sick clusters.  Read in tumor dataset. Treat healthyVector as a training set.
```{r initialiseTumorVector}
tumor = read.csv("./Data/tumor.csv", header=FALSE)
tumorMatrix = as.matrix(tumor)
tumorVector = as.vector(tumorMatrix)
```
```{r flexClustering}
#install.packages("flexclust")
library('flexclust')

KMC.kcca = as.kcca(KMC, healthyVector)

tumorClusters = predict(KMC.kcca, newdata = tumorVector)
dim(tumorClusters) = c(nrow(tumorMatrix), ncol(tumorMatrix))

image(tumorClusters, axes = F, col=rainbow(k))
```
