---
title: "XlsXmlDataTable"
author: "Lin"
date: "05/06/2015"
output: html_document
---
#Data Input and DataTable
Demonstrating the power of data table, and examples of xls and xml imports
---
set working directory and date
```{r initialize}
setwd('~/Coursera/CleanData')
dateDownloaded=date(); dateDownloaded
```
__csv from website__
Download an Internet file, read it in as csv and determine the number of million dollar houses (VAL==24, per codebook).
---
```{r readCSV}
fileUrl = 'https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv'
fileOnDisk = './Data/housing.csv'
#list.files('./Data')
download.file(fileUrl, destfile=fileOnDisk, method='curl')
houses=read.csv(fileOnDisk,header=T)
#list.files('./Data')
length(which(houses$VAL==24))
#or
table(houses$VAL)
```
__dataTable from website__
Download an Internet file, read it in as a data table and dtermine the number of million dollar houses (VAL==24, per codebook). Remember .N option in data.table.
```{r readDT}
library('data.table')
```
```{r read0}
housesDT = data.table(read.csv(fileOnDisk))
```
```{r read1}
setkey(housesDT, VAL)
housesDT[, .N, key(housesDT)]
```
__xlsx from website__
Read in R18-23 and C7-15 of gasInfo file https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx and determine sum of the column resulting from multiplying Zip by Ext (removing NAs first
```{r xlsRead}
packages = c("gdata", "xlsx")
sapply(packages, library, character.only=T, quietly=T)
fileUrl = 'https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx'
diskFile = './Data/naturalGas.xlsx'

download.file(fileUrl, destfile=diskFile, method='curl')
```
```{r extractRowsCols}
list.files('./Data')
cols=7:15; rows=18:23
natGas = read.xlsx(diskFile, sheetIndex=1, rowIndex=rows, colIndex=cols)

sum(natGas$Zip*natGas$Ext,na.rm=T) 
```
__xml from website__
In the xmldata, https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml, how many restaurants have zipcode 21231?
```{r xml}
fileUrl = "http://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
library('XML')

doc = xmlInternalTreeParse(fileUrl)
#or
#library('httr')
#doc <- xmlTreeParse(rawToChar(GET(fileUrl)$content), useInternal=TRUE)
rootNode = xmlRoot(doc)
xmlName(rootNode)
names(rootNode)
names(rootNode[[1]][[1]])
```{r results='hide'}
xmlSApply(rootNode, xmlValue)
xpathSApply(rootNode, '//zipcode', xmlValue)
length(which(xpathSApply(rootNode, '//zipcode', xmlValue)==21231))
#or 
zipcode = xpathSApply(rootNode, '//zipcode', xmlValue)
table(zipcode == 21231) 
``` 
__data.table__
fread https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv, DT it and find the fastest way to calclate the average of pwgtp15 broken down by gender
```{r dataTable checkingFunction}
library('data.table')
fileUrl='https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv'
download.file(fileUrl, destfile='./Data/chixPlus.xlsx', method='curl')
DT = fread('./Data/chixPlus.xlsx', verbose=F)

check <- function(y, t) {
    message(sprintf("Elapsed time: %.10f", t[3]))
    print(y)
}
```
checking for output validity and speed
```{r validOutputNspeed, error=T}
choice1 <- system.time(y <- DT[,mean(pwgtp15),by=SEX] ); check(y, choice1)
choice2 <- system.time(y <- rowMeans(DT)[DT$SEX==1]) + system.time(rowMeans(DT)[DT$SEX==2] ); check(y, choice2)
choice3 <- system.time(y <- tapply(DT$pwgtp15,DT$SEX,mean) ); check(y, choice3)
choice4 <- system.time(y <- mean(DT$pwgtp15,by=DT$SEX) ); check(y, choice4)
choice5 <- system.time(y <- mean(DT[DT$SEX == 1, ]$pwgtp15)) + system.time(mean(DT[DT$SEX ==2, ]$pwgtp15)); check(y, choice5)
choice6 <- system.time(y <- sapply(split(DT$pwgtp15,DT$SEX),mean) ); check(y, choice6)
check(y, choice1)
```
